Comprehensive optical and data management infrastructure for high-throughput light sheet microscopy of whole mouse brains

### 2015-02-15 latex-style-files-spie-manuscript/manuscript_Leo.tex
- method section to exclude sample preparation from optical characterisation paragraph - find out bead size and company

\author{M. Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b,f} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S. Pavone,\supscr{a,b,c,d}  }

\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy (LENS), University of Florence, Italy\\
\supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
\supscrsm{c}National Institute of Optics, National Research Council, Italy\\
\supscrsm{d}International Center for Computational Neurophotonics (ICON Foundation), Italy\\
\supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
\supscrsm{f}Distrio, Amsterdam, The Netherlands}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal connections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. We have developed a confocal light sheet microscope that has been optimised for the 3D imaging of structurally intact, clarified, whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light sheet community. The unprecedented amount of data routinely generated by light sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution allows characterization and quantification of neuronal connections in unsectioned mouse brains. 
\end{abstract}

@@

The highly ambitious project of mapping and understanding each and every neuronal connection in the whole brain has been moved from the realm of wishful longing to feasible reality by the recent advent of light sheet fluorescent microscopy (LSFM). With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate, perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap. Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise. Hence LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths.

Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast, cheap and reproducible sample preparation and mounting, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces. The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation. On the other hand, the imaging of large, intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent. This makes LSFM a truly interdisciplinary field in which the technological advances by optical developers need to be matched by novel development in the area of information and biotechnology.

Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large, clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$), immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the the control hardware and software is presented. The microscope software coordinates each and every microscope component and ensures critical timing and synchronisation between those components. The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light sheet community. We further give a systematic and robust approach to handle, store and analyse light sheet microscopy data of tens of terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets.

@@

\subsection{Laser unit}		
The custom-made, confocal light sheet microscope is equipped with 5 linearly polarised, cw lasers for fluorescence excitation (Figure\ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table\ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent, high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system. First, a low voltage, analog signal from the DAQ board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to switch to zero the output of the pre-amplifier, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing). After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

@@

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).  The galvos are on planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. A guide to align objectives to a common focus can be found in the supplementary information. The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. %cite{StelzerNatMeth2014}.
Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$. With a 200mm tube lens the field of view in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).

In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in approx. $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of

@@

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for a data acquisition and generation device (DAQ) from National Instruments which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also paragraph \ref{sec:timing} on synchronisation). Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame2.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:frame2} Schematic of sample mounting and motion. (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent, perpendicular light paths where the excitation light sheet and the detection focal plane overlap. (B) The custom-made sample chamber is assembled with silicone bellows and seal rings. The clarified, fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D). (E) Mounting of a clarified, fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.} 
   \end{figure}

We designed a cubic, water-tight sample chamber (Figure\ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large, clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Figure\ref{fig:frame2},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Figure\ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. To fill the entire volume of the sample chamber approximately 400ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table\ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Figure\ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized, clarified samples, such as mouse brains, with high resolution in whole mount preparation. While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes. The problem of sample mounting in a light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample. Most commonly the vertical direction is chosen. Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.

For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:frame2},E). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

@@

The optical properties of a microscope can be summarized by the point-spread function (PSF), which is the image of a point source in object space. In particular, the radial (i.e. perpendicular to the detection axis) and axial (i.e. parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (see Fig. \ref{fig:origin}, A). In a light sheet microscope, axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics, respectively. The radial PSF is a standard Airy function, whose FWHM is given by:

@@

$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective. The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the the depth of field of the detection objective. If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}. The radius of the beam waist is given by:

@@

where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index). Note that, for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
The axial FWHM is then given by:

@@

The thickness of the light sheet is not constant throughout the field of view (FOV) due to the limited depth of focus of the Gaussian beam. The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:

@@

The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 2.68 \micro m$. An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table\ref{tab:resolution}. The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.

@@

For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. To this end the galvo scanners were calibrated using a fluorescein solution in the sample chamber and an image of the focal line was acquired for a set of mirror angles. By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner. A linear fit to this data yielded the precise amplitude and offset for each galvo scanner hereby taking into account the confocal slit width itself such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip.

From the same data the average FWHM of the Gaussian excitation line over the FOV was calculated. The average FWHM of $0.7\micro m$ was hence set as 1 confocal unit and corresponded to a slit width of 3 horizontal lines on the camera. For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?) embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS). The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at 40 °C then mixed with a diluted bead solution and left to polymerise over night on a coverslip. The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}. The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175-70 \micro m$ in the sample space. For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg. Fig.\ref{fig:origin},A) throughout the image stack. After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths. The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig.\ref{fig:origin},B) and the lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14 \micro) m$ respectively. The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits. The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig. \ref{fig:origin},C).   
$0.61 \micro m$

@@

	Everybody take a look at Figure\ref{fig:LSMdata} because it is the best we have.

>>>>

\author{M. Caroline M\"{u}llenbroich,\supscr{a,b} Ludovico Silvestri, \supscr{a,c} Leonardo Onofri,\supscr{e} Irene Costantini,\supscr{a} Marcel van 't Hoff,\supscr{a,b} Leonardo Sacconi,\supscr{a,c} Giulio Iannello,\supscr{e} Francesco S. Pavone,\supscr{a,b,c,d}  }

\affiliation{\supscrsm{a}European Laboratory for Non-linear Spectroscopy (LENS), University of Florence, Italy\\
\supscrsm{b}Department of Physics and Astronomy, University of Florence, Italy\\
\supscrsm{c}National Institute of Optics, National Research Council, Italy\\
\supscrsm{d}International Center for Computational Neurophotonics (ICON Foundation), Italy\\
\supscrsm{e}Integrated Research Centre, University Campus Bio-Medico of Rome, Italy\\
%\supscrsm{f}Distrio, Amsterdam, The Netherlands
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal connections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. We have developed a confocal light sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light sheet community. The unprecedented amount of data routinely generated by light sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal connections in unsectioned mouse brains. 
\end{abstract}

@@

The highly ambitious project of mapping and understanding each and every neuronal connection in the whole brain has been moved from the realm of wishful longing to feasible reality by the recent advent of light sheet fluorescent microscopy (LSFM). With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal and spine features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel and affords optical sectioning by operating fluorescence excitation and detection on separate perpendicularly oriented paths where the excitation light sheet and the detection focal plane overlap. Consequently fluorophores outside the light sheet are neither bleached nor contribute blurring out-of-focus noise. Hence LSFM reduces phototoxicity and photobleaching while achieving excellent resolution at high penetration depths.

Several challenges remain to be overcome, however, to allow fast and, most of all, systematic production of reliable datasets and their meaningful interpretation to further our understanding of neuronal networks. Those challenges include fast cheap and reproducible sample preparation and mounting, automated image acquisition that does not require constant attention by an expert and, most crucially, the storage, interpretation and analysis of the unprecedented huge data sets light sheet microscopy routinely produces. The mapping and understanding of this ``big data" is a colossal task that requires the expertise of computer scientists to employ fully automated post-processing, for example, to do cell counting or blood vessel segmentation. On the other hand, the imaging of large intrinsically opaque samples in light sheet microscopy necessitates clearing protocols based on refractive index matching which render the tissue transparent. This makes LSFM a truly interdisciplinary field in which the technological advances by optical developers need to be matched by novel development in the area of information and biotechnology.

Here we will present a state-of-the-art LSFM, as it is implemented in our lab, which is especially beneficial to acquire 3D data sets of large clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the control hardware and software is presented. The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components. The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light sheet community. We further give a systematic and robust approach to handle, store and analyse light sheet microscopy data of tens of terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets. \textit{Include sentence about data if we show any.}

@@

\subsection{Laser unit}		
The custom-made confocal light sheet microscope is equipped with 5 linearly polarised cw lasers for fluorescence excitation (Fig. \ref{fig:excitation},A). The wavelengths were chosen to excite the most common fluorophores (see Table \ref{tab:optomechanics} for the manufacturer and specifications of opto-mechanical components). The laser light from each laser is first collimated and expanded with a telescope (f140, f200) and then combined into a common path with a beam steering mirror and a long-pass filter (Semrock, LaserMUX\texttrademark\ series). An acousto-optical tunable filter (AOTF) acts as fast ($\mu s$) electronically tunable filter which uses the acousto-optical interaction inside an anisotropic medium to select and transmit any combination of up to four of the laser lines. The radio-frequency applied on the AOTF transducer controls the wavelength being transmitted into the first order and the radio-frequency amplitude allows to adjust the transmitted light intensity. Due its nonlinear response we measured the AOTF light transmittance for each wavelength as a function of radio frequency amplitude and determined a look-up table to linearise the output. The zero order light is blocked by an iris. An electro-optical laser modulator (EOM) acts like a wave plate with electronically controlled retardation and rapidly rotates (few hundreds ns) the input polarisation of the excitation light by $90\degree$. The wavelength-dependent high voltage that needs to be applied to the birefringent crystal inside the modulator to change the optical path length is provided by a two-step amplification system. First, a low voltage analog signal from the data acquisition and generation (DAQ) board is pre-amplified with custom made electronics and then fed into a commercial high voltage amplifier. A digital line is used to switch the output of the pre-amplifier to zero, allowing control of the frequency with which the polarisation is changed (see also section \ref{sec:timing} on timing). After the laser modulator the excitation beam is further expanded by a factor of two with two achromatic doublets (f100, f200).

@@

Each scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance low magnification objective (Nikon, 10x 0.3NA WD 17.5mm).  The galvos are in planes conjugate with the back focal plane of their respective excitation objective to ensure that a tilt angle of the galvo converts into a lateral translation of the Gaussian beam across the specimen. The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. A guide to align objectives to a common focus can be found in the supplementary information. The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts. %cite{StelzerNatMeth2014}.
Additionally each line in specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.

@@

In its simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens form an image on a wide-field detector. We collect fluorescence with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP, effective focal length 7.2 mm). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. The cell size of the OrcaFlash is $p^2= (6.5\micro m)^2$ over an active area of $r^2= (13.3mm)^2$. With a 200mm tube lens the field of view (FOV) in the sample is $480\micro m$ (see also Table \ref{tab:resolution} for relevant formulas).

In the camera's rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor\cite{Baumgart2012}. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t_{\text{shutter}}=9.7\micro s$) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to $t_{\text{exp}}=0.3ms$ results in approx. $l=\nicefrac{t_{\text{exp}}}{t_{\text{shutter}}}\approx31$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of

@@

The camera was run as master in the internal trigger mode and a synchronisation pulse generated with the exposure of each new line was used as as an output trigger for the DAQ board which was operated as slave. The saw-tooth driving signal for the galvo mirrors was generated by the DAQ and synchronised with the pixel line reset pulses from the camera to achieve confocal line detection\cite{Baumgart2012} (see also section \ref{sec:timing} on synchronisation). Any deviation from precise synchronisation results in image artefacts and severely degraded image contrast. The confocal resolution can be changed at run-time by changing the user-defined line exposure time and with it the rolling shutter width, that is the number of horizontal pixel lines simultaneously exposed.

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{frame2.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:frame2} Schematic of sample mounting and motion. (A) Fluorescence excitation (along x axis) and detection (along z axis) are operated on independent perpendicular light paths where the excitation light sheet and the detection focal plane overlap. (B) The custom-made sample chamber is assembled with silicone bellows and seal rings. The clarified fluorescently-labelled brain is mounted on a Teflon cylinder in the centre of the watertight chamber filled with clearing solution (C) and can be translated and rotated freely with piezo motors (D). (E) Mounting of a clarified fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into the Teflon cylinder.} 
   \end{figure}

We designed a cubic water-tight sample chamber (Fig. \ref{fig:frame2},A) that allows access from all six sides while maintaining the 3D integrity of large clarified and fluorescently-labelled mouse brains. The sample chamber is tightly bolted  to the optical breadboard while soft connections using silicone bellows allow for adjustive movements of the objectives and free 3D motion of the motor stages (Fig. \ref{fig:frame2},B). All connections are sealed with rubber rings and silicone caulk and additionally tightened with cable binders. In this way the objectives can be refocused and realigned without compromising the watertight seal of the chamber (Fig. \ref{fig:frame2},C). The clarified brains are imaged immersed in clearing solution composed of 63\% TDE in Phosphate buffered saline (PBS) and a refractive index of 1.45. To fill the entire volume of the sample chamber approximately 250ml clearing solution are needed. A motorized x-, y-, z-, $\theta$-stage (Physik Instrumente, see Table \ref{tab:optomechanics}) allows free 3D motion and rotation of a Teflon cylinder which reaches into the centre of the chamber (Fig. \ref{fig:frame2},D). Illumination and detection axes are horizontal while sample rotation occurs around the vertical axis.

To elucidate neuronal projections and functional connections in structurally intact tissue it is paramount to be able to image centimeter-sized clarified samples, such as mouse brains, with high resolution in whole mount preparation. While promising clearing protocols are well documented in literature\cite{Chung2013,Tomer2014}, the question of sample preparation and mounting in light sheet microscopy is not trivial but requires novel approaches to such extent that it is becoming a separate field of research and very diverse strategies such as FEP tubes, 3D printed chambers and Quartz cuvettes have been reported\cite{Kaufmann2012,Pitrone2013,Olarte2012,Tomer2014}, however, these approaches are limited to much smaller sample volumes. The problem of sample mounting in a light sheet microscope arises form the fact that optical access to the sample is required from 3-4 planar sides leaving only two opposing sides to insert, fix and move the sample. Most commonly the vertical direction is chosen. Stable mounting is hereby a key concern as a whole brain tomography can require image acquisition in excess of 24 hours and the effects of gravity, tissue shrinking/expansion and evaporation of the clearing solution over such time spans might have to be considered.

For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Fig. \ref{fig:frame2},E). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

@@

The optical properties of a microscope can be summarised by the point-spread function (PSF), which is the image of a point source in object space. In particular, the radial (i.e. perpendicular to the detection axis) and axial (i.e. parallel to the detection axis) resolution of the microscope can be quantified with the full width at half-maximum (FWHM) of the PSF itself along the chosen direction (see Fig. \ref{fig:origin},A). In a light sheet microscope axial and radial resolution are determined by the numerical aperture (NA) of the illumination and detection optics respectively. The radial PSF is a standard Airy function whose FWHM is given by:

@@

$\lambda_0$ being the wavelength in vacuum and $\text{NA}_{\text{d}}$ the NA of the detection objective. The axial resolution is dominated by the thickness of the light sheet which for high NA detection objectives is usually larger than the depth of field of the detection objective. If Gaussian beams are used for illumination, the thickness of the light sheet can be calculated by the well-known formulas of Gaussian optics\cite{Teich}. The radius of the beam waist is given by:

@@

where $w$ is the $1/e^2$ radius of the beam entering the illumination objective, $ f_{\text{i}}^{\text{eff}}$ is the effective focal length of the illumination optics and $\lambda$ is the wavelength in the medium ($\lambda = \lambda_0 / n$, $n$ being the refractive index). Note that for air objectives (as the one we use for illumination) the effective focal length is extended by a factor $n$ when used inside a medium with refractive index different from unity\cite{Silvestri2012}.
The axial FWHM is then given by:

@@

The thickness of the light sheet is not constant throughout the FOV due to the limited depth of focus of the Gaussian beam. The latter can be quantified by the confocal parameter $b$, which is the distance along which the beam $1/e^2$ radius remains relatively constant and smaller than $\sqrt{2} w_0$:

@@

The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 2.68 \micro m$. An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table \ref{tab:resolution}. The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.

@@

For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. To this end the galvo scanners were calibrated using a fluorescein solution in the sample chamber and an image of the focal line was acquired for a set of mirror angles. By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner. A linear fit to this data yielded the precise amplitude and offset for each galvo scanner. The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip. From the same data the average FWHM of the Gaussian excitation line over the FOV was calculated. The average FWHM of $0.7\micro m$ was hence set as 1 confocal unit and corresponded to a slit width of 3 horizontal lines on the camera.

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively. The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig. \ref{fig:origin},C).

@@

	Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.
